Clustering time series based on probability distributions across temporal granularities

### 2021-11-17 main.Rmd
fig 10 solution

```{r groups-4and5, fig.cap = "Summary plots for four and five clusters showing the distribution of electricity demand combined for all members over $hod$, $moy$, and $wnwd$. Groups A-1 (customers 21-24), A-2 (customers 4-9), and A-3 (customers 10-15) profiles correspond to Groups B-1, B-2, and B-3, respectively. Cluster A-4 splits into B-4 (customers 16-20) and B-5 (customers 1-3) to produce the five clusters, which better resolves the $moy$ distribution. B-4 is characterized by higher energy consumption in the first few months of the year and more variation in weekend usage. B-5 is distinguished by higher consumption in the middle of the year (winter months) and similar weekday-weekend inter-quartile range. When $k = 4$ is used, these two groups merge to form A-4, which has a $moy$ profile of higher usage in both the beginning and middle of the year, which is not representative of the individuals in the group.", fig.height=5}

@@

```{r parcoord-application, fig.cap="Each of the $24$ customers is represented by a parallel coordinate plot (a) with four wpd-based groupings. Plot (b) which shows median $wpd$ values for each group. The plot shows that $moy$ is the most important variable in identifying clusters, whereas  $wnwd$ is the least significant and has the least fluctuation. Two customers (id: 16 and 18) with high $wpd$ across  $wnwd$ stand out in this display. Group-4 has a higher $wpd$ for $hod$ than $moy$ or  $wnwd$. Group-2 and Group-3 have the most discernible pattern across $moy$. Group-1 is a mixed group with strong patterns across at least one of the three variables. All of these could be observed from the plot or the table (b).", message=FALSE, warning=FALSE, fig.height=6}
#include_graphics("figs/parcoord-application.png")
```

>>>>

```{r groups-4and5, fig.cap = "Summary plots for four and five clusters from JS-NQT showing the distribution of electricity demand combined for all members over $hod$, $moy$, and $wnwd$. Groups A-1 (customers 21-24), A-2 (customers 4-9), and A-3 (customers 10-15) profiles correspond to Groups B-1, B-2, and B-3, respectively. Cluster A-4 splits into B-4 (customers 16-20) and B-5 (customers 1-3) to produce the five clusters, which better resolves the $moy$ distribution.", fig.height=5}

@@

```{r parcoord-application, fig.cap="Summary of the four cluster results from WPD, shown as a parallel coordinate plot and table. XXX TO BE REVISED WHEN DIFFERENT CLUSTER SOLUTION IS SHOWN", message=FALSE, warning=FALSE, fig.height=6}
#include_graphics("figs/parcoord-application.png")
```
